UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-14 paper/paper.tex
paper updates

Metrics gathered in Prerequisites section have limited knowledge about environment. Collection per job or per process produces one log line and has scope of a measurement period. Having such structured data would not let to answer machine wide neither cluster wide questions. The data has to be post-processed to allow calculation of below listed aggregations and analytics.

@@

The data will be analyzed in terms of daily usage. This requires to split metrics into buckets of one day worth of data. 
It is achieved by applying a simple filter~\ref{daily_usage} in Apache Spark.

@@

The aim for this metric is to find out how long a machine is up. It is a key metric that will be used to calculate optimality factors later on. Algorithm~\ref{alg:uptime_per_machine} represents pseudo code implementation and~\ref{uptime_per_machine_implementation} contains implementation in Python with Apache Spark.

@@

\myparagraph{Calculate intersection points to find out the best pricing scheme for a number of hours/day utilization}

\begin{algorithm}[H]
 \KwData{Array of cph for 2 pricing schemes;}
 \KwResult{Intersection point when one pricing scheme becomes cheaper than the other one;}
 read array1\;
 read array2\;
 \ForAll{cph in array} {
 	\If{$cph2 <= $cph1} {
 		return cph
 	}
 }
\caption{Calculate intersection point between two pricing schemes}
\end{algorithm}

\myparagraph{Calculate distance from optimality points based on uptime}
Input: Machine uptime per day

@@

Algorithm~\ref{alg:jobs_per_day} represents pseudo code implementation and~\ref{jobs_per_day} contains implementation in Python with Apache Spark.

>>>>

Metrics gathered in Prerequisites section have limited knowledge about environment. Collection per job or per process produces one log line and has scope of a measurement period. Such structured data itself would not answer machine wide neither cluster wide questions. The data has to be post-processed to allow calculation of below listed aggregations and analytics.

@@

The data will be analyzed in terms of daily usage. This requires to split metrics into buckets of one day worth of data. 
It is achieved by applying a simple filter from Listing~\ref{daily_usage} in Apache Spark.

@@

The aim for this metric is to find out how long a machine is up. It is a key metric that will be used to calculate optimality factors later on. Algorithm~\ref{alg:uptime_per_machine} represents pseudo code implementation and Listing~\ref{uptime_per_machine_implementation} contains implementation in Python with Apache Spark.

@@

\myparagraph{Intersection points}

This is an implementation of \textit{ip(scheme1, scheme2)} defined in Taxonomy. This metric will be a reference point that identifies optimality points based on~\textit{cph} for various schemes. Algorithm~\ref{alg:intersection points} represents pseudo code and Listing~\ref{intersection_points} shows implementation in Python.

\begin{algorithm}[H]
 \label{alg:intersection points}
 \KwData{Array of cph for 2 pricing schemes;}
 \KwResult{Intersection point when one pricing scheme becomes cheaper than the other one;}
 read array1\;
 read array2\;
 \ForAll{cph in array} {
 	\If{$cph2 <= $cph1} {
 		return cph
 	}
 }
\caption{Calculate intersection point between two pricing schemes}
\end{algorithm}

\begin{minipage}{\linewidth}
\begin{lstlisting}[label={intersection_points},caption={Intersection point between various pricing schemes},frame=single] 
def _calc_intersection_point(self, first, second):
   for i in range(len(first)):
      if (second[i] <= first[i]):
         return i
\end{lstlisting}
\end{minipage}

\myparagraph{Calculate distance from optimality points based on uptime}

This metric represents either positive or negative value to indicate distance from intersection points calculated

Input: Machine uptime per day

@@

Number of jobs per day will be a useful parameter to calculate cluster-wide averages used for suggestions. Algorithm~\ref{alg:jobs_per_day} represents pseudo code implementation and~\ref{jobs_per_day} contains implementation in Python with Apache Spark.
